\chapter{Actors and requirements}\label{ch:requirements}

Main actors:
\begin{itemize}
	\item The \standout{Administrator};
	\item The \standout{Users}.
\end{itemize}

\section{Functional requirements}\label{sec:functionalrequirements}

\begin{itemize}
	\item Privileges: The application must handle users with different privileges
	\item Strategy Development: The user must be able to develop a strategy, the application will provide a Library with utility functions that can be used during the development of the Strategy
	\item Strategy Sharing: The user must be able to share their strategies and to retrieve strategy developed from other users.
	\item Multiple Markets: The application must provide the user multiple Markets among which he/she can choose in order to apply the strategy.
	\item Report: After the simulation of the Strategy is over the application must provide to the user a Report in which he can find several statistics on the behaviour of the Strategy. The report must be persistently stored by the application, so that a user can retrieve these reports every time he/she need.
	\item Data Providers: The application must have the capability to retrieve new data in different manners: manually from the administrator, or directly from other services thanks to API or Scraping.
	\item Administration functionalities: The application must have functionalities for administrators. An administrator must be able to add/remove/delete data from the application, enable and disable data sources, limit the submission rate of a user, enable/disable data streaming from data sources. \footnote{Other examples of administration functionalities can be seen in \ref{ch:specs}}
\end{itemize}

\section{Non-functional requirements}\label{sec:nonfunctionalrequirements}

\begin{itemize}
	\item Availability: The application must be always available, users need to connect from every location at any time.
	\item Network Partition Tolerance: The application must handle failures in the network, preferring the availability to the consistency. In fact the application core business is to simulate trading strategies on a large period of time, so even if some recent data is not consistently updated at any time it's preferable to keep serving the users instead of blocking the operations. 
	\item Concurrency: The application must handle multiple clients concurrently connected.
	\item Persistency: Data must be persistently stored by the application.
\end{itemize}
